---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# `proj.verse`

[![Project Status: Active – The project has reached a stable, usable state and is being actively developed.](https://www.repostatus.org/badges/latest/active.svg)](https://www.repostatus.org/#active)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/patter)](https://CRAN.R-project.org/package=patter)

[`proj.verse`](https://github.com/edwardlavender/proj.verse) is an umbrella package for a series of `proj` packages that support scientific project development and management in `R`:

- [`proj.build`](https://github.com/edwardlavender/proj.build) provides build tools for functions and packages;
- [`proj.file`](https://github.com/edwardlavender/proj.file) provides file-system tools;
- [`proj.templates`](https://github.com/edwardlavender/proj.templates) sets up template RStudio Projects;
- [`proj.lapply`](https://github.com/edwardlavender/proj.lapply) provides iterative project workflows;

# Installation

The [`proj.verse`](https://github.com/edwardlavender/proj.verse) family of packages can be installed with: 

```{r, eval = FALSE}
install.packages("devtools")
devtools::install_github("edwardlavender/proj.verse", 
                         dependencies = TRUE)
```

# Code of conduct

Please note that the [`proj.verse`](https://github.com/edwardlavender/proj.verse) project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/1/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.